|

### 2018-12-18 Paper 2019.Rmd
Trying to understand gitignore again

```{r CRI output to table}
stargazer(cri.base.pooled, 
          cri.limits.pooled, 
          cri.limits.fixed,
          cri.limits.fixed.time, 
          type="text",
          title = "Are the presence or amounts of campaign limits correlated with the Corruption Reflections Index?",
          out="collateral/CRI.htm",
          dep.var.labels = "Corruption Convictions Index",
          covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)","Divided government","Binding one-term limit","Binding two-term limit","Real per capita income ($1000)","AUSAs per million population","Unemployment","Citizen ideology measure","Percent high school graduates","Real per capita gov revenues ($1000)","Inequality: Male wages","Relative government wages","Urbanization","Log of population (millions)"),
          add.lines = list(c("Effects","Pooled","Pooled","Fixed","Two-Way"))
          )
```
### Model II: Difference-in-Difference Model
<!--Add specification, formulas?-->
Even if the panel models above fail to capture correlation between state level campaign finance laws and corruption arrests, it could be the case that changes in campaign finance laws, rather than relative campaign finance limits, are correlated with decreases in corruption. A difference-in-difference regression can help identify this by comparing the state-years in which campaign finance laws changed to state-years where they remained constant. If tighter campaign finance laws are correlated with lower corruption levels, then a change in one year should lead to lower corruption convictions in the years following.

@@

<!-- Old code
```{r panel modeling, eval=F}
## CCI 
# Individual limits and corruption
CCIreg1  <- plm(CCI ~ ind_limits_2010*ind_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
# No signifigance

@@

```{r (old) controlled panel modeling, eval=F}
#Next: Panel model of corruption against unemployment and high school? 
testmodel01 <- plm(CCI ~ rpcinc_annual_new + unemp + high_school + logNumpop + citi6006 + grelimp, data = AltBarber, index = c("st","year"), effect="twoways")

@@

```{r controlled panel modeling, eval=F}

@@

```{r post-Lentz panel effects modeling 1, eval=F}
# Include lagged dependent variables here. 
# Erin's question: Are these "pooled"? 
# Her effort to understand: Write out the formulas. 
# Maybe helpful? https://onlinecourses.science.psu.edu/stat502/node/162/
# Erin's suggestion https://www.princeton.edu/~otorres/Panel101R.pdf
# On robust standard errors https://stats.stackexchange.com/questions/117052/replicating-statas-robust-option-in-r
# And https://cran.r-project.org/web/packages/sandwich/vignettes/sandwich.pdf
# And https://www.brodrigues.co/blog/2018-07-08-rob_stderr/, 
# Pretty good explanation here https://www.methodsconsultants.com/tutorial/introduction-to-random-effects-models-including-hlm/
# Go through this? https://github.com/tyleransom/EconometricsLabs/blob/master/tidyRcheatsheet.pdf
summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC))
summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways"))
summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), model="within", effect="twoways"))
summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), model="within"))
summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), model="random")) #FAIL 
summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC), model="pooling")
summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC), model="within")

@@

```{r stargazer CCI latex, results="asis", eval=TRUE}
stargazer(CCIreg1, CCIreg2, CCIreg3, CCIreg5,
  type="latex", 
  title = "Are campaign limits and corruption convictions correlated?",
  dep.var.labels = c("Corruption Convictions Index"),
  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"),
  font.size = "small",
  header=FALSE,
  column.sep.width = "-15pt",
  digits = 2, digits.extra = 2)
```

@@

```{r stargazer CRI latex, results="asis", eval=TRUE}
stargazer(CRIreg1, CRIreg2, CRIreg3, CRIreg5,
          type="latex",
  title = "Are campaign limits and corruption reflections correlated?",
  dep.var.labels = c("Corruption Reflections Index"),
  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"),
  font.size = "small",
  header=FALSE,
  column.sep.width = "-15pt",
  digits = 2, digits.extra = 2)
```

```{r stargazer controlled panel, eval=F}
stargazer(CCIcontrol01,CCIcontrol02,CRIcontrol01,CRIcontrol02,
  type="text", 
  title = "Are campaign limits and correlated with corruption convictions or reflections?",
  out="collateral/CCICRIcontrol.htm",
  dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
  covariate.labels=c("Divided government", "Binding one-term limit"," Binding two-term limit","Real per capita income ($1000)","AUSAs per million population","Unemployment","Citizen ideology measure","Percent high school graduates","Real per capita gov revenues ($1000)","Inequality: Male wages","Relative government wages","Urbanization","Log of population (millions)","Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)")
  )
```

```{r 3 stargazer controlled panel latex, results="asis", eval=TRUE}
stargazer(CCIcontrol01,CCIcontrol02,CRIcontrol01,CRIcontrol02,
  title = "Are campaign limits and correlated with corruption convictions or reflections?",
  dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
  covariate.labels=c("Divided government", "Binding one-term limit"," Binding two-term limit","Real per capita income (thousands)","AUSAs per million population","Unemployment","Citizen ideology measure","Percent high school graduates","Real per capita gov revenues (thousands)","Inequality: Male wages","Relative government wages","Urbanization","Log of population (millions)","Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"),
  font.size = "small",
  header=FALSE,
  column.sep.width = "-15pt",
  no.space = T,
  digits = 2, digits.extra = 2)
```

@@

\blandscape
```{r stargazer DiD latex, results="asis", eval=TRUE}
stargazer(CCIDID01, CCIDID02, CCIDID03, CRIDID01, CRIDID02, CRIDID03,
  title = "Do changes in limits lead to lower levels of corruption?",
  dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
  covariate.labels=c("Individual limits removed","Individual limits imposed","Individual limit amount","Individual limits removed*amount","Individual limits imposed*amount",
                     "PAC limits removed","PAC limits imposed","PAC limit amount","PAC limits removed*amount","PAC limits imposed*amount",
                     "Individual-to-party limits removed","Individual-to-party limits imposed","Individual-to-party limit amount","Individual-to-party limits removed*amount","Individual-to-party limits imposed*amount"),
  font.size = "small", 
  header = FALSE,
  column.sep.width = "-15pt",
  digits = 2, digits.extra = 2,
  no.space = TRUE)

>>>>

```{r CRI output to table}
stargazer(cri.base.pooled, 
          cri.limits.pooled, 
          cri.limits.fixed,
          cri.limits.fixed.time, 
          type="text",
          title = "Are the presence or amounts of campaign limits correlated with the Corruption Reflections Index?",
          out="collateral/CRI.htm",
          dep.var.labels = "Corruption Convictions Index",
          covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)","Divided government","Binding one-term limit","Binding two-term limit","Real per capita income ($1000)","AUSAs per million population","Unemployment","Citizen ideology measure","Percent high school graduates","Real per capita gov revenues ($1000)","Inequality: Male wages","Relative government wages","Urbanization","Log of population (millions)"),
          add.lines = list(c("Effects","Pooled","Pooled","Fixed","Two-Way"))
          ) 
```

### Model II: Difference-in-Difference Model
<!--Add specification, formulas?-->
Even if the panel models above fail to capture correlation between state level campaign finance laws and corruption arrests, it could be the case that changes in campaign finance laws, rather than relative campaign finance limits, are correlated with decreases in corruption. A difference-in-difference regression can help identify this by comparing the state-years in which campaign finance laws changed to state-years where they remained constant. If tighter campaign finance laws are correlated with lower corruption levels, then a change in one year should lead to lower corruption convictions in the years following.

@@

<!-- Old code
```{r panel modeling}
## CCI 
# Individual limits and corruption
CCIreg1  <- plm(CCI ~ ind_limits_2010*ind_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
# No signifigance

@@

```{r (old) controlled panel modeling}
#Next: Panel model of corruption against unemployment and high school? 
testmodel01 <- plm(CCI ~ rpcinc_annual_new + unemp + high_school + logNumpop + citi6006 + grelimp, data = AltBarber, index = c("st","year"), effect="twoways")

@@

```{r controlled panel modeling}

@@

```{r post-Lentz panel effects modeling 1}
# Include lagged dependent variables here. 
# Erin's question: Are these "pooled"? 
# Her effort to understand: Write out the formulas. 
# Maybe helpful? https://onlinecourses.science.psu.edu/stat502/node/162/
# Erin's suggestion https://www.princeton.edu/~otorres/Panel101R.pdf
# On robust standard errors https://stats.stackexchange.com/questions/117052/replicating-statas-robust-option-in-r
# And https://cran.r-project.org/web/packages/sandwich/vignettes/sandwich.pdf
# And https://www.brodrigues.co/blog/2018-07-08-rob_stderr/, 
# Pretty good explanation here https://www.methodsconsultants.com/tutorial/introduction-to-random-effects-models-including-hlm/
# Go through this? https://github.com/tyleransom/EconometricsLabs/blob/master/tidyRcheatsheet.pdf
summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC))
summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways"))
summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), model="within", effect="twoways"))
summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), model="within"))
summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), model="random")) #FAIL 
summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC), model="pooling")
summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC), model="within")

@@

```{r stargazer CCI latex, results="asis"}
stargazer(CCIreg1, CCIreg2, CCIreg3, CCIreg5,
  type="latex", 
  title = "Are campaign limits and corruption convictions correlated?",
  dep.var.labels = c("Corruption Convictions Index"),
  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"),
  font.size = "small",
  header=FALSE,
  column.sep.width = "-15pt",
  digits = 2, digits.extra = 2)
```

@@

```{r stargazer CRI latex, results="asis"}
stargazer(CRIreg1, CRIreg2, CRIreg3, CRIreg5,
          type="latex",
  title = "Are campaign limits and corruption reflections correlated?",
  dep.var.labels = c("Corruption Reflections Index"),
  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"),
  font.size = "small",
  header=FALSE,
  column.sep.width = "-15pt",
  digits = 2, digits.extra = 2)
```

```{r stargazer controlled panel}
stargazer(CCIcontrol01,CCIcontrol02,CRIcontrol01,CRIcontrol02,
  type="text", 
  title = "Are campaign limits and correlated with corruption convictions or reflections?",
  out="collateral/CCICRIcontrol.htm",
  dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
  covariate.labels=c("Divided government", "Binding one-term limit"," Binding two-term limit","Real per capita income ($1000)","AUSAs per million population","Unemployment","Citizen ideology measure","Percent high school graduates","Real per capita gov revenues ($1000)","Inequality: Male wages","Relative government wages","Urbanization","Log of population (millions)","Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)")
  )
```

```{r 3 stargazer controlled panel latex, results="asis"}
stargazer(CCIcontrol01,CCIcontrol02,CRIcontrol01,CRIcontrol02,
  title = "Are campaign limits and correlated with corruption convictions or reflections?",
  dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
  covariate.labels=c("Divided government", "Binding one-term limit"," Binding two-term limit","Real per capita income (thousands)","AUSAs per million population","Unemployment","Citizen ideology measure","Percent high school graduates","Real per capita gov revenues (thousands)","Inequality: Male wages","Relative government wages","Urbanization","Log of population (millions)","Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"),
  font.size = "small",
  header=FALSE,
  column.sep.width = "-15pt",
  no.space = T,
  digits = 2, digits.extra = 2)
```

@@

\blandscape
```{r stargazer DiD latex, results="asis"}
stargazer(CCIDID01, CCIDID02, CCIDID03, CRIDID01, CRIDID02, CRIDID03,
  title = "Do changes in limits lead to lower levels of corruption?",
  dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
  covariate.labels=c("Individual limits removed","Individual limits imposed","Individual limit amount","Individual limits removed*amount","Individual limits imposed*amount",
                     "PAC limits removed","PAC limits imposed","PAC limit amount","PAC limits removed*amount","PAC limits imposed*amount",
                     "Individual-to-party limits removed","Individual-to-party limits imposed","Individual-to-party limit amount","Individual-to-party limits removed*amount","Individual-to-party limits imposed*amount"),
  font.size = "small", 
  header = FALSE,
  column.sep.width = "-15pt",
  digits = 2, digits.extra = 2,
  no.space = TRUE)
